Main Figures

### 2021-02-19 figure_manuscript/codes_of_figures.Rmd
Updating manuscript figure codes

```{r, include=FALSE, message=FALSE, warning=FALSE}
library(janitor)
library(tidyverse)
library(purrr)
library(readr)
library(biomaRt)
library(TCGAbiolinks)
library(ceRNAnetsim)
library(dplyr)
library(ggVennDiagram)
library(ggraph)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
#knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(cache=FALSE)
```

@@

mirtarbase_node_perturbations <- readRDS("mirtarbase_node_perturbations.RDS") # data includes results of find_node_perturbation() function for tumor and normal samples of each patient.

@@

significant_node_graph%>%
  bind_rows(gene_top_annotation_graph)%>%
  as_tbl_graph()%>%
  mutate(type = ifelse(startsWith(name, "hsa"), "KEGG", "GO"),
         type = ifelse(startsWith(name, "hsa-"), "miRNA", type),
         type = ifelse(startsWith(name, "ENSG"), "Gene", type))%>%
  mutate(centrality= centrality_degree(mode = "all"),
         annotation = ifelse(name %in% gene_top_annotation_graph$Ensembl_Gene_Id, "Enriched Genes", "other"))%>%
  left_join(hg19, by =c("name"="ensembl_gene_id"))%>%
  filter( type %in% c("miRNA", "Gene"))%>%
  ggraph(layout = "kk")+ 
  geom_edge_link(colour = "seashell2")+
  geom_node_point(color = "seashell2")+
  geom_node_point(aes(filter= annotation == "Enriched Genes", size = centrality, color = "Enriched Genes"), shape = 16)+
  geom_node_point(aes(filter= type == "miRNA", color = "miRNA"), shape = 17, size = 2)+
  geom_node_point(aes(filter= type == "GO", size = centrality, color = "GO"), shape = 18)+
  geom_node_point(aes(filter= type == "KEGG", size = centrality, color = "KEGG"), shape = 15)+
  theme_graph(base_family = "sans")+
  geom_node_text(aes(filter= name %in% top_important, label = hgnc_symbol), size =3.5, repel = TRUE)+
  theme(plot.margin = margin(0, 0, 0, 0, "cm"), legend.position = "none")+
  guides(size=FALSE, shape = FALSE)+
  scale_color_manual(name = "Node types", values = c("Enriched Genes" = "sandybrown", "miRNA"= "dodgerblue2", "GO"= "green", "KEGG"= "red"))

>>>>

```{r, include=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(purrr)
library(readr)
library(biomaRt)
library(TCGAbiolinks)
library(ceRNAnetsim)
library(ggVennDiagram)
library(ggraph)
library(janitor)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
#knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(cache=FALSE)
```

@@

mirtarbase_node_perturbations <- readRDS("mirtarbase_node_perturbations.RDS") 
# data includes results of find_node_perturbation() 
#function for tumor and normal samples of each patient.

@@

significant_node_graph%>%
  bind_rows(gene_top_annotation_graph)%>%
  as_tbl_graph()%>%
  mutate(type = ifelse(startsWith(name, "hsa"), "KEGG", "GO"),
         type = ifelse(startsWith(name, "hsa-"), "miRNA", type),
         type = ifelse(startsWith(name, "ENSG"), "Gene", type))%>%
  mutate(centrality= centrality_degree(mode = "all"),
         annotation = ifelse(name %in% gene_top_annotation_graph$Ensembl_Gene_Id, "Enriched Genes", "other"))%>%
  left_join(hg19, by =c("name"="ensembl_gene_id"))%>%
  filter( type %in% c("miRNA", "Gene"))-> annotation_graph

annotation_graph%>%
  ggraph(layout = "kk")+ 
  geom_edge_link(colour = "seashell2")+
  geom_node_point(color = "seashell2")+
  geom_node_point(aes(filter= annotation == "Enriched Genes", 
                      size = centrality, color = "Enriched Genes"), 
                  shape = 16)+
  geom_node_point(aes(filter= type == "miRNA", color = "miRNA"), 
                  shape = 17, 
                  size = 2)+
  geom_node_point(aes(filter= type == "GO", size = centrality, color = "GO"), 
                  shape = 18)+
  geom_node_point(aes(filter= type == "KEGG", size = centrality, color = "KEGG"), 
                  shape = 15)+
  theme_graph(base_family = "sans")+
  geom_node_text(aes(filter= name %in% top_important, label = hgnc_symbol), 
                 size =3.5, 
                 repel = TRUE)+
  theme(plot.margin = margin(0, 0, 0, 0, "cm"), legend.position = "none")+
  guides(size=FALSE, shape = FALSE)+
  scale_color_manual(name = "Node types", 
                     values = c("Enriched Genes" = "sandybrown",
                                "miRNA"= "dodgerblue2",
                                "GO"= "green", "KEGG"= "red"))

Note: Alternatively, network can also be visualized by using Cytoscape (v 3.8.2) and Rcy3 package from Bioconductor.

```{r, eval=FALSE}
annotation_graph
#BiocManager::install("RCy3")

library(RCy3)

# After starting cytoscape at desktop, following commands are run:

RCy3::cytoscapePing()
createNetworkFromIgraph(annotation_graph)
